Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2023-11-20 manuscript/manuscript.qmd
Add extra BJPS statements

>>>>

# Data availability statement

All data and replication code is available at `DATAVERSE DOI` and at `OSF DOI`.

# Supplementary material

A companion statistical analysis notebook with a fuller description of the data, modeling details and diagnostics, and additional explanations of the Bayesian multinomial modeling approach, along with links to the data and replication code, is available at `ANONYMIZED URL/DOI`.

# Funding

This research received no external funding.

# Competing interests

The authors report there are no competing interests to declare.
